Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-06-16 sas2015/content/concl.tex
adding techreport and paper

Previous algorithms for data-flow analysis are unable to avoid propagating
data-flow facts along infeasible paths that arise in the presence of
correlated polymorphic method calls. 
% 
We present an approach for transforming an IFDS problem into an IDE problem
in which path feasibility is encoded into functions associated
with edges in an exploded control-flow supergraph. The solution to this
IDE problem can be mapped back to the solution space of the original IFDS
problem, and is more precise for some client programs because data flow along
infeasible paths is prevented. We present a formalization of the
transformation, prove its correctness, and briefly report on
preliminary experiments with our prototype implementation. Full proof
details are available in the Appendix,
and we plan to submit our implementation and experimental data to the
artifact evaluation committee. 
%  
As future work, it is possible to adapt our approach to work on IDE
problems. We would convert an initial IDE problem into a more complex IDE problem, 
such that the solution of the latter generates a more precise
solution to former, by preventing data flow along infeasible paths.

>>>>

Previous algorithms for data-flow analysis are unable to avoid propagating
data-flow facts along infeasible paths that arise in the presence of
correlated polymorphic method calls. 
% 
We present an approach for transforming an IFDS problem into an IDE problem
in which path feasibility is encoded into functions associated
with edges in an exploded control-flow supergraph. The solution to this
IDE problem can be mapped back to the solution space of the original IFDS
problem, and is more precise for some client programs because data flow along
infeasible paths is prevented. We present a formalization of the
transformation, prove its correctness, and briefly report on
preliminary experiments with our prototype implementation. Full proof
details are available in the \reportOrAppendix,
and we plan to submit our implementation and experimental data to the
artifact evaluation committee. 
%  
As future work, it is possible to adapt our approach to work on IDE
problems. We would convert an initial IDE problem into a more complex IDE problem, 
such that the solution of the latter generates a more precise
solution to former, by preventing data flow along infeasible paths.

### 2015-06-16 sas2015/content/impl.tex
adding techreport and paper

All of the basic micro-functions defined in Definition~\ref{def:microfn} can be expressed
in this representation. The following lemmas show how function comparison, composition, and meet can be implemented using basic set operations
on $I$ and $U$.
The proofs of all of the lemmas and theorems are in the Appendix.

@@

>>>>

All of the basic micro-functions defined in Definition~\ref{def:microfn} can be expressed
in this representation. The following lemmas show how function comparison, composition, and meet can be implemented using basic set operations
on $I$ and $U$.
The proofs of all of the lemmas and theorems are in the \reportOrAppendix.

@@

The equivalence analysis is there for two reasons: 
(i)  to explain how a correlated-calls-IDE problem can be derived from an IDE problem that has the same meaning as the original IFDS problem, and 
(ii) to provide a base line against which to compare the efficiency of the correlated-calls analysis.

We compare the efficiency of the correlated-calls analysis against the equivalence-IDE analysis instead of the IFDS analysis because the time complexities of an IFDS and an equivalent IDE analysis are the same: an equivalent IDE analysis is just an IFDS analysis in which all edges are labeled with identity micro functions, and all operations on those functions are optimized to be constant-time.

### 2015-06-16 sas2015/content/intro.tex
review comments
corrections
adding techreport and paper

The remainder of this paper is organized as follows.
%
Section~\ref{sec:MotivatingExample} presents a motivating example.
%
Section~\ref{sec:bg} reviews the IFDS and IDE algorithms.
%
Section~\ref{sec:cca} presents the correlated-calls transformation,
sketches a proof of its correctness,%
\footnote{
  Detailed proofs of our lemmas and theorems can be found in
  the appendix.
} and discusses our implementation.
%
%Our implementation is discussed in Section~\ref{sec:Evaluation}.
%
Related work is discussed in Section~\ref{sec:Related}.
%
Finally, Section~\ref{sec:Conclusions} presents conclusions and directions for future work.

>>>>

The remainder of this paper is organized as follows.
%
Section~\ref{sec:MotivatingExample} presents a motivating example.
%
Section~\ref{sec:bg} reviews the IFDS and IDE algorithms.
%
Section~\ref{sec:cca} presents the correlated-calls transformation, 
states the correctness properties%
\footnote{
  Detailed proofs of our lemmas and theorems can be found in
  the \reportOrAppendix.
}, and discusses our implementation.
%
%Our implementation is discussed in Section~\ref{sec:Evaluation}.
%
Related work is discussed in Section~\ref{sec:Related}.
%
Finally, Section~\ref{sec:Conclusions} presents conclusions and directions for future work.
